Tail Indices and Scale Parameters in Financial Time Series

### 2017-03-29 papers/FX/draft.tex
Revised the draft of FX.

First notice that when $b = 0$, $\mathcal U(F, \phi)$ reduces to
$\E u(C(X, \phi))$. Only the first integral of \eqref{eq:t1} remains.
Its integrand becomes $\ln[C(x, \phi) C(-x, \phi)]$.
Now observe $\ln(C(x, \phi)C(-x, \phi))$ is an increasing function of
$x$:
\begin{eqnarray*}
  \pd{C(x, \phi) C(-x, \phi)}{x}
  &=&
  \phi e^r (1 - \phi) (e^x - e^{-x}) > 0
\end{eqnarray*}
Thus when $b = 0$, by 1st case of remark \ref{remark:I} and lemma
\ref{lemma:II},
$\pd{\mathcal U(F, \phi))}{\nu} < 0$ for all $\phi$. Hence all
investors guided by this utility function would be seeking the
smallest $\nu$, i.e. the heaviest tail in the market.

However, this is not necessarily the case when $b > 0$. For example,
consider the case when $q = 0$ and $\hat\phi = 1$. This may be
viewed an approximation to the situation where the interest rate $r$ is
vanishingly low while the investor is more conservative than
greedy. In this case we have
\begin{eqnarray*}
  \mathcal U(F, \phi) = \int_{0}^{\infty} e^{-b x} f(x, \nu) dx
\end{eqnarray*}
Thus by the 1st case of lemma \ref{lemma:I} and lemma \ref{lemma:II},
$\opd{\nu}\mathcal U(F, \phi) > 0$. In this extreme case, the investor
would rather seek the largest $\nu$ or in other words, the lightest
tail in the market.

\subsubsection{power-utility function}
In this section we consider the case when the utility function
$u(\cdot)$ takes the form
\[
u(C) = -{1 \over \xi} C^{-\xi}
\]
Another major difference caused by a non-zero value of $b$ is seen in
the value of $\hat\phi$. When $b = 0$, $\hat\phi$ increases
continuously with $\nu$ as shown in figure \ref{fig:phi_hat_t5e-1};
when $b > 0$, $\hat\phi$ instead increases by jumping up at a sequence
of values of $\nu$. This is shown in figure \ref{fig:phi_hat_b_t5e-1}.
\begin{figure}[htb!]
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_t5e-1.pdf}
    \caption{$\hat\phi$ when $b = 0$}
    \label{fig:phi_hat_t5e-1}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_b_t5e-1.pdf}
    \caption{$\hat\phi$ when $b = 0.01$}
    \label{fig:phi_hat_b_t5e-1}
  \end{subfigure}
  \caption{$\hat\phi$, the optimal equity allocation when the utility
    function is $u(C) = -{2 \over \sqrt{C}}$
  }
\end{figure}

>>>>

First notice that when $b = 0$, $\mathcal U(F, \phi)$ reduces to
$\E u(C(X, \phi))$. Only the first integral of \eqref{eq:t1} remains.
Its integrand becomes $\ln[C(x, \phi) C(-x, \phi)]$.
Now observe $\ln(C(x, \phi)C(-x, \phi))$ is an increasing function of
$x$:
\begin{eqnarray*}
  \pd{C(x, \phi) C(-x, \phi)}{x}
  &=&
  \phi e^r (1 - \phi) (e^x - e^{-x}) > 0
\end{eqnarray*}
Thus when $b = 0$, by 1st case of remark \ref{remark:I} and lemma
\ref{lemma:II},
$\pd{\mathcal U(F, \phi))}{\nu} < 0$ for all $\phi$. Hence all
investors guided by this utility function would be seeking the
smallest $\nu$, i.e. the heaviest tail in the market. Here note that
Student's t is a symmetric distribution; heavier tails imply greater
down-side risk as well as greater up-side potential.

In fact, even when $b > 0$, the same monotonicity property holds. This
is revealed by numerically maximizing $\mathcal U(F, \phi)$ with
respect to $\phi$ for a sequence of selected values of $\nu$. The
results are shown in figures \ref{fig:phi_hat_t_log} and
\ref{fig:U_b_t_log}.
\begin{figure}[htb!]
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_b_t_log.pdf}
    \caption{$\hat\phi(\nu)$ of log-utility function}
    \label{fig:phi_hat_t_log}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{U_b_t_log.pdf}
    \caption{$G(\nu)$ of log-utility function}
    \label{fig:U_b_t_log}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_b_t_power.pdf}
    \caption{$\hat\phi(\nu)$ of power-utility function}
    \label{fig:phi_hat_t_power}
  \end{subfigure}
  \begin{subfigure}[b]{0.5\linewidth}
    \includegraphics[width=\textwidth]{U_b_t_power.pdf}
    \caption{$G(\nu)$ of power-utility function}
    \label{fig:U_b_t_power}
  \end{subfigure}
  \caption{$\hat\phi$ and $G(\nu)$
  }
\end{figure}

%% However, this is not necessarily the case when $b > 0$. For example,
%% consider the case when $q = 0$ and $\hat\phi = 1$. This may be
%% viewed an approximation to the situation where the interest rate $r$ is
%% vanishingly low while the investor is more conservative than
%% greedy. In this case we have
%% \begin{eqnarray*}
%%   \mathcal U(F, \phi) = \int_{0}^{\infty} e^{-b x} f(x, \nu) dx
%% \end{eqnarray*}
%% Thus by the 1st case of lemma \ref{lemma:I} and lemma \ref{lemma:II},
%% $\opd{\nu}\mathcal U(F, \phi) > 0$. In this extreme case, the investor
%% would rather seek the largest $\nu$ or in other words, the lightest
%% tail in the market.

\subsubsection{power-utility function}
In this section we consider the case when the utility function
$u(\cdot)$ takes the form
\[
u(C) = -{1 \over \xi} C^{-\xi}
\]
One can see from figure \ref{fig:phi_hat_t_power} and
\ref{fig:U_b_t_power} that both $\hat \phi$ and $G(\nu)$ are monotonically 
decreasing with $\nu$ as in the case of a log-utility function.
%% \begin{figure}[htb!]
%%   \begin{subfigure}[b]{0.5\linewidth}
%%     \includegraphics[width=\textwidth]{phi_hat_b_t_power.pdf}
%%     \caption{$\hat\phi(\nu)$}
%%     \label{fig:phi_hat_t_power}
%%   \end{subfigure}
%%   \begin{subfigure}[b]{0.5\linewidth}
%%     \includegraphics[width=\textwidth]{U_b_t_power.pdf}
%%     \caption{$G(\nu)$}
%%     \label{fig:U_b_t_power}
%%   \end{subfigure}
%%   \caption{$\hat\phi$ and $G(\nu)$ when the utility
%%     function is $u(C) = -{2 \over \sqrt{C}}$
%%   }
%% \end{figure}
